Bayesian beta regressions with brms in R: A tutorial for phoneticians

### 2025-02-10 manuscript/manuscript.qmd
render pdf and html

---
title: A tutorial of Bayesian beta regressions with brms in R
author:
  - name: Stefano Coretta
    email: s.coretta@ed.ac.uk
    affiliations: 
        - id: uoe
          name: University of Edinburgh
          department: Linguistics and English Language
          address: 3 George Sq
          city: Edinburgh
          state: United Kingdom
          postal-code: EH8 9AD
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Paul Bürkner
    email: paul.buerkner@gmail.com
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: 
  - linguistics.bib
  - statistics.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: authoryear
execute:
  cache: true
---

>>>>

---
title: "Bayesian beta regressions with brms in R: A tutorial for phoneticians"
author:
  - name: Stefano Coretta
    email: s.coretta@ed.ac.uk
    affiliations: 
        - id: uoe
          name: University of Edinburgh
          department: Linguistics and English Language
          address: 3 George Sq
          city: Edinburgh
          state: United Kingdom
          postal-code: EH8 9AD
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Paul Bürkner
    email: paul.buerkner@gmail.com
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: 
  - linguistics.bib
  - statistics.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: authoryear
  elsevier-html: default
execute:
  cache: true
---

### 2025-02-10 manuscript/manuscript.tex
render pdf and html

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A tutorial of Bayesian beta regressions with brms in R},
  pdfauthor={Stefano Coretta; Paul Bürkner},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{A tutorial of Bayesian beta regressions with brms in R}
\author[1]{Stefano Coretta%
\corref{cor1}%
\fnref{fn1}}
 \ead{s.coretta@ed.ac.uk} 
\author[]{Paul Bürkner%
%
}
 \ead{paul.buerkner@gmail.com}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Bayesian beta regressions with brms in R: A tutorial for phoneticians},
  pdfauthor={Stefano Coretta; Paul Bürkner},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Bayesian beta regressions with brms in R: A tutorial for
phoneticians}
\author[1]{Stefano Coretta%
\corref{cor1}%
\fnref{fn1}}
 \ead{s.coretta@ed.ac.uk} 
\author[]{Paul Bürkner%
%
}
 \ead{paul.buerkner@gmail.com}
